Bird beak's elaboration and exploration

### 2021-08-03 Analysis/08.1-Number_of_dimensions_old.Rmd
Updated dimensions analyses

```{r, echo = FALSE, print = FALSE}
library(beer)
library(MCMCglmm)
data(chara_data)
data(chara_tree)
```

@@

## Get the PCA
load("MCMCglmm_covar/full_PCAs.rda")

## Selecting axis function
# @params strict whether to have less than the threshold (strict) or at least the threshold (false)
select.axis <- function(ordination, threshold = 0.99, group, details = FALSE, strict = FALSE) {
    ## Set the group
    if(missing(group)) {
        group <- list(rownames(ordination))
    }

>>>>

```{r, echo = FALSE, print = FALSE}
library(dispRity)
library(beer)
library(MCMCglmm)
data(chara_data)
data(chara_tree)
```

@@

## Get the PCA
load("MCMCglmm_covar/full_PCAs.rda")
```

```{r}
## Selecting axis function
# @params strict whether to have less than the threshold (strict) or at least the threshold (false)
select.axis <- function(ordination, threshold = 0.99, group, details = FALSE, strict = FALSE) {
    ## Set the group
    if(missing(group)) {
        group <- list(rownames(ordination))
    }
